Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-06 cosmic_voids.tex
2 ultimos parrafos de la introduccion revisados

Once we establish the FA as a conveniente tracer for voids, we proceed to
identify individual voids as basins of local minima. For this purpose we
implement a \textit{watershed transform algorithm}
\citep{Beucher79,Beucher93} which has been already implemented on void
finding schemes\citep{Platen07,Neyrinck08} defining voids as catching
basins of local minima of the density field.  
We use insted minima of the FA field to find define the voids.

This paper is organized as follows. 
In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
we use to find the cosmic web in N-body simulations. 
Then in Section \ref{sec:bulk_voids} we explain in detail our void
finder based on the fractional anisotropy of the tidal and shear
tensor fields. 
In Section \ref{sec:experiments} we describe the setup
for the numerical experiments we perform to show the performance of
the new void finding technique. 
Our results are presented in \ref{sec:results} to finally comment and
conclude about this findings in Section \ref{sec:conclusions}.

>>>>

Once we establish the FA as a void tracer, we proceed to
identify individual voids as basins of local minima. 
For this we implement a \textit{watershed transform algorithm}
\citep{Beucher79,Beucher93} which has been used to define as catching
basins of local minima of the density field
\citep{Platen07,Neyrinck08}; we use insted minima of the FA field to
find define the voids.

This paper is organized as follows. 
In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
we use to find the cosmic web in N-body simulations. 
Then in Section \ref{sec:bulk_voids} we explain in detail our void
finder based on the fractional anisotropy of the tidal and shear
tensor fields. 
In Section \ref{sec:experiments} we describe the numerical experiments
we perform to show the performance of the new void finding technique.  
Our results are presented in \ref{sec:results} to finally comment and
conclude about these findings in Section \ref{sec:conclusions}.
